Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming

### 2020-09-15 Paper/Manuscript_Stats&Comp/manuscript_STCO.tex
update manuscript and supplemental material

\institute{Gabriel Riutort-Mayol \at
              Department of Cartographic Engineering, Geodesy, and Photogrammetry, Universitat Polit\`ecnica de Val\`encia, Spain\\
              \email{gabriuma@gmail.com}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           Paul-Christian Bürkner \at
              Department of Computer Science, University of Stuttgard, Germany \\
              \emph{Most of work was done while at Aalto University}
           \and
           Michael R.\ Andersen \at
              Department of Applied Mathematics and Computer Science, Technical University of Denmark, Denmark
           \and
           Arno Solin \at
              Department of Computer Science, Aalto University, Finland
           \and
           Aki Vehtari \at
              Department of Computer Science, Aalto University, Finland
}

>>>>

\institute{Gabriel Riutort-Mayol \at
              Department of Cartographic Engineering, Geodesy, and Photogrammetry, Universitat Polit\`ecnica de Val\`encia, Spain\\
              \email{gabriuma@gmail.com}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           Paul-Christian Bürkner \at
              Excellence Cluster for Simulation Technology, University of Stuttgart, Germany \\
              \emph{Most of work was done while at Dept. of Computer Science at Aalto University}
           \and
           Michael R.\ Andersen \at
              Department of Applied Mathematics and Computer Science, Technical University of Denmark, Denmark
           \and
           Arno Solin \at
              Department of Computer Science, Aalto University, Finland
           \and
           Aki Vehtari \at
              Department of Computer Science, Aalto University, Finland
}
